Analyzing X-ray images in Python with scikit-image

### 2016-08-19 skimage_tomo.tex
Wrote conclusion section

\section*{Challenges and roadmap}

@@

@@

\section*{Competing interests}
: The authors declare that the research was conducted
in the absence of any commercial or financial relationships that could be
construed as a potential conflict of interest.

>>>>

@@

\texttt{scikit-image} offers a wide variety of image processing
algorithms, using a simple interface natively compatible with 2D and 3D
images. It is well integrated into the Scientific Python ecosystem, so
that it interfaces well with visualization libraries or other data
processing packages. \texttt{scikit-image} has seen a tremendous growth
since its creation in 2010, both in terms of users and proposed features.
In addition to the growing number of scientific teams that use
\texttt{scikit-image} for processing X-ray-modalities images,
domain-specific tools are now using \texttt{scikit-image} as a dependency
to build upon. Examples include \texttt{tomopy} \citep{Gursoy2014} for
tomographic reconstruction, or \texttt{DIOPTAS} \citep{Prescher2015} for
the reduction and exploration of X-ray diffraction data. It is likely
that more application-specific softwares will benefit from depending on
\texttt{scikit-image} in the future, since \texttt{scikit-image} strives
to be domain-agnostic and to keep a stable interface. On the end-user
side, future work includes a better integration of parallel processing
capabilities, completion of full 3-D compatibility, an enriched narrative
documentation, and the extension of the number of algorithms.

@@

\section*{Competing interests}
The authors declare that the research was conducted
in the absence of any commercial or financial relationships that could be
construed as a potential conflict of interest.
